Proportional multi-state multiple-cohort life table model

### 2018-04-03 MSLT/MSLTdoc.Rmd
Added packages to include citations

output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in

@@

The model was developed by Jan Barendregt and colleagues (REF ACE prevention and core papers) and has been widely used in Australia and New Zealand (Ref ACE-report and BODE website of key publications).

@@

>>>>

output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in
  citation_package: natib
  bibliography: Bibliography.bib

@@

The model was developed by Jan Barendregt and colleagues  and has been widely used in Australia and New Zealand ().

@@

#References
